---
title: "Scrape IDPH data"
date: "Compiled at `r format(Sys.time(), '%Y-%m-%d %H:%M:%S', tz = 'UTC')` UTC"
output: github_document
params:
  name: "02-scrape-idph" # change if you rename file
---

```{r here, message=FALSE}
here::i_am(paste0(params$name, ".Rmd"), uuid = "357772d2-af9d-4d6e-868f-3dc08773181c")
```

The purpose of this document is ...

```{r packages}
library("conflicted")
library("rvest")
library("tibble")
library("dplyr")
library("here")
library("fs")
library("stringr")
library("readr")
library("purrr")
```

```{r directories}
# create or *empty* the target directory, used to write this file's data: 
projthis::proj_create_dir_target(params$name, clean = FALSE)

# function to get path to target directory: path_target("sample.csv")
path_target <- projthis::proj_path_target(params$name)

# function to get path to previous data: path_source("00-import", "sample.csv")
path_source <- projthis::proj_path_source(params$name)
```

## Tasks

Next we define some local functions. 

First, a function that, given the HTML for the state's page, returns the date tag embedded in the page.

```{r}
extract_date <- function(html) {
  
  text <- html_text(html)
  
  str_date_year <- str_extract(text, "\\d{1,2}/\\d{1,2}/\\d{4}")[[1]]
  str_date_no_year <- str_extract(text, '\\d{1,2}/\\d{1,2}(?= )')[[1]]
  str_date <- NA_character_
  
  if (!is.na(str_date_year)) {
    str_date <- str_date_year
  }
  
  if (!is.na(str_date_no_year)) {
    str_date <- glue::glue("{str_date_no_year}/2020")
  }
  
  date <- readr::parse_date(str_date, format = "%m/%d/%Y")
  
  date
}
```

Next, a function that, given the HTML, returns a data-frame with: 

- `date`
- `county`
- `tests`
- `cases`
- `recovered`
- `deaths`

All values are cumulative.

```{r}
iowa_county_meta <- 
  read_csv(
    path_source("01-county-metadata", "iowa_county_meta.csv")
  )
```

```{r}
extract_data <- function(html, date) {
  content <-
    html %>%
    rvest::html_nodes("td") %>%
    purrr::map_chr(rvest::html_text)
  
  ind_counties <- 
    which(
      content %in% iowa_county_meta$county |
      str_detect(content, regex("^pending", ignore_case = TRUE))  
    )
  
  iowa_data <- 
    tibble::tibble(
      date = date,
      county = content[ind_counties],
      tests = as.numeric(content[ind_counties + 1]),
      cases = as.numeric(content[ind_counties + 2]),
      recovered = as.numeric(content[ind_counties + 3]),
      deaths = as.numeric(content[ind_counties + 4])
    ) %>%
    dplyr::mutate(
      tests = ifelse(is.na(tests), 0, tests),
      cases = ifelse(is.na(cases), 0, cases),
      recovered = ifelse(is.na(recovered), 0, recovered),
      deaths = ifelse(is.na(deaths), 0, deaths),
    ) %>% 
    dplyr::left_join(
      iowa_county_meta %>% dplyr::select(fips, county),
      by = "county"
    ) %>%
    dplyr::select(date, fips, county, everything())
    
  
  iowa_data
}
```

A function that, given a directory, returns a named vector of candidate files:

```{r}
get_date_files <- function(dir) {
  
  regex_date <- ".*access-(\\d{4}-\\d{2}-\\d{2})\\.(csv|html)$"
  
  files <- dir_ls(dir, regexp = regex_date)
  dates <- str_replace(files, regex_date, "\\1")
  
  names(files) <- dates
  
  files
} 
```

Let's determine the HTML files we need to scrape; these are the files that do not have corresponding CSV files in the target directory.

```{r}
files_source <- get_date_files(path_source("00-import", "idph-html"))
files_target <- 
  get_date_files(path_target()) %>%
  head(-1) # always parse the most-recent file
dates_needed <- 
  names(files_source)[!names(files_source) %in% names(files_target)]
files_needed <- files_source[dates_needed]
files_needed
```

Finally, we need a function, given a filepath to an html file, and a target directory, scrape the html file and write a CSV file in the target directory.

```{r}
write_file <- function(file_html, dir_target) {
  
  html <- xml2::read_html(file_html)
  date <- extract_date(html)
  data <- extract_data(html, date)
  
  readr::write_csv(
    data, 
    path = fs::path(dir_target, glue::glue("access-{date}.csv"))
  )
}
```

Test some of our functions:

```{r}
html <- read_html(path_source("00-import", "idph-html", "access-2020-06-22.html"))
date <- extract_date(html)
```

```{r}
data <- extract_data(html, date)
print(data)
```

Finally, create the new CSV files.

```{r}
walk(files_needed, write_file, path_target())
```

## Files written

These files have been written to the target directory, ```r paste0("data/", params$name)```:

```{r list-files-target}
projthis::proj_dir_info(path_target()) %>% 
  arrange(desc(path)) # show most-recent first
```
